\subsection{Application parts}\label{sec:implAppParts}
As presented in \cref{fig:appDesign} the application consist of a set data flow where different type of data is being collected and then transmitted to the server.
This sub-section will describe these different parts.

\subsubsection{Beacon readings}\label{sec:implAppPartsBeacons}
To be able to collect nearby \acrshort{ble} beacons (\cref{sec:theoryBleiBeacons}) the signals from them need to be collected in the application.

\bigskip

With help of the native Apple API \textit{CoreLocation} \cite{...} nearby beacon signals is being collected and can be processed further by the application.
Since the beacons data is being used across the application the initialization of the reading need to be made at the application top level.

\subsubsection{Beacon RSSI data}\label{sec:implAppPartsRssi}
From the beacons data the \acrshort{rssi} values can be extracted to form a fingerprint.
This fingerprint is being used to position the device in the server.

\subsubsection{HTTP(S) POST request}\label{sec:implAppPartsPostReq}
To be able to use the data form the device in the server it need to be send away from the device.
The data is being send to a API endpoint in the server with the help of HTTPs post requests \cite{...}.
To use this in the application the Apple API \textit{ResourceURL} \cite{...} is used.

\bigskip

The body of the post request is the collected \acrshort{rssi} values from the beacons, which is \acrfull{json} \cite{IntroducingJSON} formatted.

\subsubsection{HTTP(s) POST response}\label{sec:implAppPartsPostRes}



