\section{Architecture}\label{sec:implArchitecture}
To fully understand the implementation of this project some architectural descriptions is needed.
This section will present different techniques and architectures used in this implementation.


\subsection{Machine}\label{sec:implArchitectureMachine}
A machine is being defines as some kind of equipment places around a industrial hall in a manufacturing environment.
This could for example be a waterpump or electrical engine that drives a stone crusher.
A machine in this work it only a set of data collections in a database and not a real physical machine.


\subsection{Group}\label{sec:implArchitectureGroup}
A group in the system is what's being located with the positioning.
The system sets up invisible boundaries in a undefined spaced out in a production hall.
When a device is being located by the system a group will be yield back instead of a physical exact position.
Machines are tied to these created groups where the machines data will be shown when the group is positioned.


\subsection{Device}\label{sec:implArchitectureDevice}
A device refer to a mobile hand held device that's in this work is a Apple iPhone 12 pro.
This device is running the developed application.


\subsection{Beacons}\label{sec:implArchitectureBeacons}
A beacon, also mentioned as iBeacon is the transmitting hardware used to position a device with de developed system.


\subsection{Server}\label{sec:implArchitectureServer}
All calculations is being taken care of by a server.
This server is not being hosted to any cloud service or a physical server in a data center, instead it is running on a local computer where the device will communicate with the server only in the same LAN.


\subsection{Frontend vs. backend}\label{sec:implArchitectureFrontBack}
In the developed \acrshort{ips} there is two major parts, a front- and backend.
The application is defined as the frontend of the system since this is the part that a user will interact with and get data presented to it. 
The backend in the developed server software that takes care of all calculations and data predictions, and delivers this to the frontend which is being presented to the user.


\subsection{API}\label{sec:implArchitectureApi}
An API is the data connection between a device and a server.
Data it sent form the device to the server via specific API \textit{endpoints} that is being defined in the application and created in the server.
The developed API works in two different types of requests, POST and GET.

\bigskip

In a POST request from the device to the server the device is giving some kind of data to the server, that is being processed by it.
When the server is done processing a response is being yield back to the device with either some resulting data or just a success message.

\bigskip

In a GET request the server is only asked to give data back to the device without any data being sent to the server.
When these different endpoints is being called form the device the server will perform various processes depending on how the API is developed.

