\section{Research analysis and problem definition}\label{sec:methodProblemDefinitionResAnalysis}
To fulfil goal \ref{goal:fieldInvestigation} and \ref{goal:systemDesign} presented in \cref{sec:introGoals} a problem definition, in the form of a case study, and a research analysis was performed.

\subsection{Problem definition}\label{sec:methodProblemDefinition}
To succeed with a project a clear understanding of the problem is a large factor.
Discussions with the customer is therefore important to create a deep understanding of the problem.
Without this knowledge a project will almost always fail.
\cite{SecretsSuccessfulSimulation1995}

\bigskip

\mt{This project was faced towards the company LKAB, and their positioning problem mentioned in the overall aim and problem statement for this thesis project.}
Meetings was conducted with the company to fully know what they wanted to solve.
This resulted in a requirement's specification which can be seen in appendix \ref{appendix:requirements}.

\subsection{Research analysis}\label{sec:methodResearchAnalysis}
\mt{The research analysis was performed as a literature review on previously made research in the area.
Only scientific resources in the form of white papers and conference publications were used in this analysis.
The gained information about previously implemented positioning systems was used as a support in the implementation in this thesis project.
The chosen techniques were the ones that showed the best results in the implemented positioning systems.}
\Cref{sec:theoryRelatedWork} presents the results from the literature review.
