\section{Software design}\label{sec:methodSoftwareDesign}
Although software design is a iterative process that can change over time, it's an important step to conduct before the development starts. \cite{EngineeringDesignIts1989, ImportanceBusinessProcess2008}

\bigskip

When the software is being designed before implemented, obvious obstacles could be avoided and therefore save time, which is important in these kinds of projects.
So this was an important part to get right from the beginning because of the time frame for the project.

\bigskip

\mt{The software was designed based on two factors, the accumulated knowledge how to design an \acrshort{ips} based on performed research analysis, and the requirements from the research analysis.}
See appendix \ref{appendix:requirements} for the resulting requirement's specification.


\subsection{Design motivation}\label{sec:methodDesignMotivation}
Motivation of the design choices is being presented in this sub-section.


\subsubsection{Classification method}\label{sec:methodSoftwareDesignClassification}
The classification algorithm used to position the device in this work fell on \acrfull{knn}, because it showed the best result in comparisons to \acrlong{ann} and \acrlong{svm}, mentioned in \cref{sec:theoryRelatedWork}.
It's also easier to implement and together with the benefits it was the best choice.


\subsubsection{Fingerprint structure}\label{sec:methodSoftwareDesignFingerprint}
\mt{In the conducted literature review  all the reviewed papers used \acrfull{rssi} based fingerprints to position the devices.
This together with its relative high accuracy in an \acrshort{ips}, and the way the system is designed in this thesis, the choice fell on \acrshort{rssi} fingerprints.}


\subsubsection{Mobile platform}\label{sec:methodSoftwareDesignMobilePlatform}
\mt{LKAB uses the Apple iPhone as their mobile platform.
To develop an \acrfull{poc} application that can be used in LKAB's system the chosen platform therefore fell on Apple iPhone.}


\subsubsection{Database}\label{sec:methodSoftwareDesignDatabase}
The database used in the \acrshort{poc} application in the Cosmos Database by Azure \cite{IntroductionAzureCosmos}.
This is a two part motivation.

\bigskip

First because LKAB use Azure to their current Infohub application described in \cref{sec:introBackground}.
So to mimic their current architecture the choice fell on an Azure based database.

\bigskip

Secondly, Cosmos, which is a NoSQL database, was used to save time since a table structure nor table relations needed to be taken into consideration.
This was well suited in this project since both the relation between the data and what each data collection was going to include was hard to decide pre-hand.


\subsubsection{Data processing}\label{sec:methodSoftwareDesignData}
The calculation of the data and the determination of the position can be done in two different ways.
Either in a centralized manner where all the data is being processed directly on the device, or at a decentralized server.
As being presented in \cref{sec:theoryRelatedWork} different approaches has been taken in different \acrshort{ips} implementations.

\bigskip

In this thesis the choice fell for a decentralized strategy that use a server to perform all data processing.
This opens up for a more flexible system since the server takes care of the data and the device just send data to, and retrieve data from, the server.


\subsubsection{Transmitters}\label{sec:methodSoftwareDesignTransmitters}
The transmitting technique chosen in this work was \acrfull{ble} beacons where the beacons had support for Apple's iBeacon protocol.
This choice depended on two different factors.

\bigskip

The first reason is limitations in Apple's iOS platform.
A developed application can only read data from the WiFi the device is connected to.
Reading of all nearby WiFi's can only be done if the application has access to a closed internal iOS API \cite{NEHotspotHelperAppleDeveloper}.
To gain access to this API Apple need to be contacted for permission.
Access is only given in special cases, such as for applications that will help a user to find nearby WiFi networks \cite{TechnicalQA1942IOS}.
This makes it impossible to fetch information from other WiFi \acrshort{ap}´s than the one connected to the device, which can only be one at a time.
With this hardware limitation the transmitting choice fell on \acrshort{ble} beacons since these can be scanned without any special permission with the iOS API \textit{CoreLocation}.

\bigskip

\mt{The second reason was that there was no access to a sufficiently large WiFi network to perform the software tests.}
A \acrshort{ble} Beacon network is easy and fairly cheep to implement and has a large flexibility on how to position the beacons.
WiFi \acrshort{ap}'s is often permanent mounted and is therefore hard to move.
It's also hard to expand the network if needed.


\subsubsection{Defined localization space}\label{sec:methodSoftwareDesignDefinedSpace} The defined space that was to be located in the system is a group.
These groups are being created together with a set of mapped fingerprints as well as a set of machines.
When the \acrshort{ips} positions the device the group is what's being located, and the machines tied to the group is being presented to the user.
Groups are used to be able to position two or more machines at the same location without the need to map each machine separately, which is required according to point \ref{req:createGroups} in the requirement specification, located in appendix \ref{appendix:requirements}.
